parental migration and adolescents educational performance

### 2022-06-11 data/Gu-thesis-script.Rmd
school and county info

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
```

@@

```{r}
d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

>>>>

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
```

@@

Detect outliers
```{r}
d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
```
